Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-30 appendix.tex
tex

\textbf{Societal Impact}.
%
As encouraged by the author guidelines, we briefly discuss the potential
societal impact of our work.
%
Adversarial attacks may raise security considerations on deep learning
applications, and hence may have negative impact.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact.
%
Besides, although adversarial training is not environment-friendly due to its
high training cost in GPU time, our study has significantly improved the
adversarial training efficiency compared to the previous works.

\textbf{Limitations}.
%
\begin{quote}

>>>>

\textbf{Societal Impact.}
%
As encouraged by the author guidelines, we briefly discuss the potential
societal impact of our work.
%
Adversarial attacks may raise \uline{security considerations} on deep learning
applications, and even cause negative effect.
%
In contrast, in this manuscript, we focus on defending against the attacks and
enhancing a model's adversarial robustness, and hence is expected to have a
positive impact instead.
%
Besides, although adversarial training is not \uline{environment-friendly} due
to its high training cost in GPU time, our study has significantly improved the
adversarial training efficiency compared to the previous works.

\textbf{Limitations.}
%
\begin{quote}

### 2021-10-30 robdml.tex
tex

>>>>

To figure out the efficacy of HM with $H_\mathcal{D}$ calculated from benign
triplets, we adversarialy train models dataset using $\text{HM}[\mathcal{R},
\mathcal{M}]$ and $\text{HM}[\mathcal{S}, \mathcal{M}]$ on the CUB dataset,
with varying PGD steps, \ie, $\eta\in\{2,4,8,16,32\}$, respectively.
%
The results can be found in \cref{tab:hmeff}.
%
The performance of the state-of-the-art defense, \ie, ACT~\cite{robrank} is
also provided as a baseline.
%
ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training
triplet is sampled using Random and Softhard strategy, respectively.
%
